Phylodynamic inference of contact network parameters through approximate Bayesian computation

### 2016-04-28 doc/thesis/appendix.Rnw
Draft???

\begin{figure}[H]
  \centering
  \includegraphics{kernel-alpha-crossv.pdf}
  \caption{
    Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{alpha} for eight epidemic scenarios. Solid lines and points are
    $R^2$ of tree kernel \gls{kSVR} under various kernel meta-parameters.
    Dashed and dotted lines are $R^2$ of linear regression against Sackin's
    index, and \gls{SVR} using \gls{nltt}.
  }
  \label{fig:alphacrossv}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{kernel-I-crossv.pdf}
  \caption{
    Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{I} for eight epidemic scenarios. Solid lines and points are $R^2$ of
    tree kernel \gls{kSVR} under various kernel meta-parameters. Dashed and
    dotted lines are $R^2$ of linear regression against Sackin's index, and
    \gls{SVR} using \gls{nltt}.
  }
  \label{fig:Icrossv}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{kernel-m-crossv.pdf}
  \caption{
    Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{m} for eight epidemic scenarios. Solid lines and points are $R^2$ of
    tree kernel \gls{kSVR} under various kernel meta-parameters. Dashed and
    dotted lines are $R^2$ of linear regression against Sackin's index, and
    \gls{SVR} using \gls{nltt}.
  }
  \label{fig:mcrossv}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{kernel-N-crossv.pdf}
  \caption{
    Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{N} for eight epidemic scenarios. Solid lines and points are $R^2$ of
    tree kernel \gls{kSVR} under various kernel meta-parameters. Dashed and
    dotted lines are $R^2$ of linear regression against Sackin's index, and
    \gls{SVR} using \gls{nltt}.
  }
  \label{fig:Ncrossv}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics{gridsearch-alpha-point-estimate.pdf}
  \caption{
      Point estimates of preferential attachment power \gls{alpha} of
      \acrlong{BA} network model, obtained on simulated trees with
      kernel-score-based grid search. Test trees were simulated according to
      several values of \gls{alpha} ($x$-axis) with other model parameters
      fixed at \gls{m} = 2, \gls{N} = 5000, and \gls{I} = 1000. The test trees
      were compared to trees simulated along a narrowly spaced grid of
      \gls{alpha} values using the tree kernel, with the same values of the
      other parameters. The grid value with the highest median kernel score was
      taken as a point estimate for \gls{alpha} ($y$-axis).
  }
  \label{fig:gridptalpha}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{gridsearch-I-point-estimate.pdf}
  \caption{
      Point estimates of prevalence at time of sampling \gls{I} of \acrlong{BA}
      network model, obtained on simulated trees with kernel-score-based grid
      search. Test trees were simulated according to several values of \gls{I}
      ($x$-axis) with other model parameters fixed at \gls{alpha} = 1, \gls{m}
      = 2, and \gls{N} = 5000. The test trees were compared to trees simulated
      along a narrowly spaced grid of \gls{I} values using the tree kernel,
      with the same values of the other parameters. The grid value with the
      highest median kernel score was taken as a point estimate for \gls{I}
      ($y$-axis).
  }
  \label{fig:gridptI}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{gridsearch-m-point-estimate.pdf}
  \caption{
      Point estimates of number of edges per vertex \gls{m} of \acrlong{BA}
      network model, obtained on simulated trees with kernel-score-based grid
      search. Test trees were simulated according to several values of \gls{m}
      ($x$-axis) with other model parameters fixed at \gls{alpha} = 1, \gls{I}
      = 1000, and \gls{N} = 5000. The test trees were compared to trees
      simulated along a narrowly spaced grid of \gls{m} values using the tree
      kernel, with the same values of the other parameters. The grid value with
      the highest median kernel score was taken as a point estimate for \gls{m}
      ($y$-axis).
  }
  \label{fig:gridptm}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{gridsearch-N-point-estimate.pdf}
  \caption{
      Point estimates of number of edges per vertex \gls{N} of \acrlong{BA}
      network model, obtained on simulated trees with kernel-score-based grid
      search. Test trees were simulated according to several values of \gls{N}
      ($x$-axis) with other model parameters fixed at \gls{alpha} = 1, \gls{m}
      = 2, and \gls{I} = 1000. The test trees were compared to trees simulated
      along a narrowly spaced grid of \gls{N} values using the tree kernel,
      with the same values of the other parameters. The grid value with the
      highest median kernel score was taken as a point estimate for \gls{m}
      ($y$-axis).
  }
  \label{fig:gridptN}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{abc-point-estimate-m3.pdf}
  \caption{                                              
    \Acrlong{MAP} point estimates for \gls{BA} model parameters obtained by
    running \software{netabc} on simulated data. Values shown are for
    simulations with \gls{m} = 3. Dashed lines indicate true values. (A)
    Estimates of \gls{alpha} and \gls{I} which were varied in these simulations
    against known values. (B) Estimates of \gls{m} and \gls{N} which were held
    fixed in these simulations at the values \gls{m} = 3 and \gls{N} = 5000.
  }        
  \label{fig:abcptm3}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{abc-point-estimate-m4.pdf}
  \caption{                                              
    \Acrlong{MAP} point estimates for \gls{BA} model parameters obtained by
    running \software{netabc} on simulated data. Values shown are for
    simulations with \gls{m} = 4. Dashed lines indicate true values. (A)
    Estimates of \gls{alpha} and \gls{I} which were varied in these simulations
    against known values. (B) Estimates of \gls{m} and \gls{N} which were held
    fixed in these simulations at the values \gls{m} = 4 and \gls{N} = 5000.
  }        
  \label{fig:abcptm4}
\end{figure}

@@

@@

\begin{figure}[ht]
  \includegraphics{realdata-hpd-bc-m2}
  \vspace{8pt}
  \caption{
      Maximum \textit{a posteriori} point estimates and 95\% HPD intervals for
      parameters of the BA network model, fitted to five published HIV datasets
      with kernel-ABC. $x$-axes indicate regions of nonzero prior density. In
      particular, the prior on $m$ was DiscreteUniform(2, 5).
  }
  \label{fig:abchpdm2}
\end{figure}

\begin{figure}[H]
  \includegraphics{bctree-posterior}
  \caption{
      Posterior distribution of BA model parameters for BC data. Vertical lines
      indicate maximum \textit{a posteriori} estimates, and shaded areas are
      95\% highest posterior density intervals. $x$-axis indicates regions of
      nonzero prior density.
  }
  \label{fig:bctree}
\end{figure}

\begin{figure}[H]
  \includegraphics{cuevas2009-posterior}
  \caption{
      Posterior distribution of BA model parameters for
      \textcite{cuevas2009hiv} data. Vertical lines indicate maximum \textit{a
      posteriori} estimates, and shaded areas are 95\% highest posterior
      density intervals. $x$-axis indicates regions of nonzero prior density.
  }
  \label{fig:cuevas}
\end{figure}

\begin{figure}[H]
  \includegraphics{li2015-posterior}
  \caption{
      Posterior distribution of BA model parameters for \textcite{li2015hiv}
      data. Vertical lines indicate maximum \textit{a posteriori} estimates,
      and shaded areas are 95\% highest posterior density intervals. $x$-axis
      indicates regions of nonzero prior density.
  }
  \label{fig:li}
\end{figure}

\begin{figure}[H]
  \includegraphics{niculescu2015-posterior}
  \caption{
      Posterior distribution of BA model parameters for
      \textcite{niculescu2015recent} data. Vertical lines indicate maximum
      \textit{a posteriori} estimates, and shaded areas are 95\% highest
      posterior density intervals. $x$-axis indicates regions of nonzero prior
      density.
  }
  \label{fig:niculescu}
\end{figure}

\begin{figure}[H]
  \includegraphics{novitsky2014-posterior}
  \caption{
      Posterior distribution of BA model parameters for
      \textcite{novitsky2013phylogenetic, novitsky2014impact} data. Vertical
      lines indicate maximum \textit{a posteriori} estimates, and shaded areas
      are 95\% highest posterior density intervals. $x$-axis indicates regions
      of nonzero prior density.
  }
  \label{fig:novitsky}
\end{figure}

\begin{figure}[H]
  \includegraphics{wang2015-posterior}
  \caption{
      Posterior distribution of BA model parameters for
      \textcite{wang2015targeting} data. Vertical lines indicate maximum
      \textit{a posteriori} estimates, and shaded areas are 95\% highest
      posterior density intervals. $x$-axis indicates regions of nonzero prior
      density.
  }
  \label{fig:wang}
\end{figure}

<<abc_posterior, echo=FALSE, results="asis">>=
    N <- 5000
    replicate <- 0
    for (m in c(2, 3, 4)) {
    for (I in c(1000, 2000)) {
    for (alpha in c(0, 0.5, 1, 1.5)) {
        fn <- sprintf("{abc-posterior/%.1f_%d_%d_%d_%d}.pdf", alpha, I, m, N, replicate)
        lab <- sprintf("fig:%.1f-%d-%d-%d-%d", alpha, I, m, N, replicate)
        cat("\\begin{figure}[H]\n")
        cat("\\centering\n")
        cat(paste0("\\includegraphics{", fn, "}\n"))
        cat(sprintf("\\caption[Approximate marginal posterior distributions of BA model parameters for a simulated transmission tree with $\\alpha$ = %.1f, $I$ = %d, $m$ = %d, and $N$ = %d]{\n", alpha, I, m, N))
        cat(sprintf("Approximate marginal posterior distributions of BA model parameters obtained by applying \textit{netabc} to a simulated transmission tree with BA parameter values $alpha$ = %.1f, $I$ = %d, $m$ = %d, and $N$ = %d. Vertical dashed lines indicate true values. Shaded areas are 95\\%% highest posterior density intervals. $x$-axes indicate regions of nonzero prior density.\n", alpha, I, m, N))
        cat("}\n")
        cat(paste0("\\label{", lab, "}\n"))
        cat("\\end{figure}\n")
        cat("\\clearpage\n\n")
    }
    }
    }
@

>>>>

\begin{figure}[H]
  \centering
  \includegraphics{kernel-alpha-crossv.pdf}
  \caption[Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{alpha} for eight epidemic scenarios.]
  {
    Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{alpha} for eight epidemic scenarios. Solid lines and points are
    $R^2$ of tree kernel \gls{kSVR} under various kernel meta-parameters.
    Dashed and dotted lines are $R^2$ of linear regression against Sackin's
    index, and \gls{SVR} using \gls{nltt}.
  }
  \label{fig:alphacrossv}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{kernel-I-crossv.pdf}
  \caption[Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{I} for eight epidemic scenarios.]
  {
    Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{I} for eight epidemic scenarios. Solid lines and points are $R^2$ of
    tree kernel \gls{kSVR} under various kernel meta-parameters. Dashed and
    dotted lines are $R^2$ of linear regression against Sackin's index, and
    \gls{SVR} using \gls{nltt}.
  }
  \label{fig:Icrossv}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{kernel-m-crossv.pdf}
  \caption[Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{m} for eight epidemic scenarios.]
  {
    Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{m} for eight epidemic scenarios. Solid lines and points are $R^2$ of
    tree kernel \gls{kSVR} under various kernel meta-parameters. Dashed and
    dotted lines are $R^2$ of linear regression against Sackin's index, and
    \gls{SVR} using \gls{nltt}.
  }
  \label{fig:mcrossv}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{kernel-N-crossv.pdf}
  \caption[Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{N} for eight epidemic scenarios.]
  {
    Cross validation accuracy of classifiers for \gls{BA} model parameter
    \gls{N} for eight epidemic scenarios. Solid lines and points are $R^2$ of
    tree kernel \gls{kSVR} under various kernel meta-parameters. Dashed and
    dotted lines are $R^2$ of linear regression against Sackin's index, and
    \gls{SVR} using \gls{nltt}.
  }
  \label{fig:Ncrossv}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics{gridsearch-alpha-point-estimate.pdf}
  \caption[
      Point estimates of preferential attachment power \gls{alpha} of
      \acrlong{BA} network model, obtained on simulated trees with
      kernel-score-based grid search.]
  {
      Point estimates of preferential attachment power \gls{alpha} of
      \acrlong{BA} network model, obtained on simulated trees with
      kernel-score-based grid search. Test trees were simulated according to
      several values of \gls{alpha} ($x$-axis) with other model parameters
      fixed at \gls{m} = 2, \gls{N} = 5000, and \gls{I} = 1000. The test trees
      were compared to trees simulated along a narrowly spaced grid of
      \gls{alpha} values using the tree kernel, with the same values of the
      other parameters. The grid value with the highest median kernel score was
      taken as a point estimate for \gls{alpha} ($y$-axis).
  }
  \label{fig:gridptalpha}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{gridsearch-I-point-estimate.pdf}
  \caption[ Point estimates of prevalence at time of sampling \gls{I} of
      \acrlong{BA} network model, obtained on simulated trees with
      kernel-score-based grid search. ]
  {
      Point estimates of prevalence at time of sampling \gls{I} of \acrlong{BA}
      network model, obtained on simulated trees with kernel-score-based grid
      search. Test trees were simulated according to several values of \gls{I}
      ($x$-axis) with other model parameters fixed at \gls{alpha} = 1, \gls{m}
      = 2, and \gls{N} = 5000. The test trees were compared to trees simulated
      along a narrowly spaced grid of \gls{I} values using the tree kernel,
      with the same values of the other parameters. The grid value with the
      highest median kernel score was taken as a point estimate for \gls{I}
      ($y$-axis).
  }
  \label{fig:gridptI}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{gridsearch-m-point-estimate.pdf}
  \caption[
      Point estimates of number of edges per vertex \gls{m} of \acrlong{BA}
      network model, obtained on simulated trees with kernel-score-based grid
      search.
  ]
  {
      Point estimates of number of edges per vertex \gls{m} of \acrlong{BA}
      network model, obtained on simulated trees with kernel-score-based grid
      search. Test trees were simulated according to several values of \gls{m}
      ($x$-axis) with other model parameters fixed at \gls{alpha} = 1, \gls{I}
      = 1000, and \gls{N} = 5000. The test trees were compared to trees
      simulated along a narrowly spaced grid of \gls{m} values using the tree
      kernel, with the same values of the other parameters. The grid value with
      the highest median kernel score was taken as a point estimate for \gls{m}
      ($y$-axis).
  }
  \label{fig:gridptm}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{gridsearch-N-point-estimate.pdf}
  \caption[
      Point estimates of number of edges per vertex \gls{N} of \acrlong{BA}
      network model, obtained on simulated trees with kernel-score-based grid
      search.
  ]{
      Point estimates of number of edges per vertex \gls{N} of \acrlong{BA}
      network model, obtained on simulated trees with kernel-score-based grid
      search. Test trees were simulated according to several values of \gls{N}
      ($x$-axis) with other model parameters fixed at \gls{alpha} = 1, \gls{m}
      = 2, and \gls{I} = 1000. The test trees were compared to trees simulated
      along a narrowly spaced grid of \gls{N} values using the tree kernel,
      with the same values of the other parameters. The grid value with the
      highest median kernel score was taken as a point estimate for \gls{m}
      ($y$-axis).
  }
  \label{fig:gridptN}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{abc-point-estimate-m3.pdf}
  \caption[
    \Acrlong{MAP} point estimates for \gls{BA} model parameters obtained by
    running \software{netabc} on simulated data, for simulations with \gls{m} = 3.
  ]{
    \Acrlong{MAP} point estimates for \gls{BA} model parameters obtained by
    running \software{netabc} on simulated data, for simulations with \gls{m} = 3.
    Dashed lines indicate true values. (A) Estimates of \gls{alpha} and \gls{I}
    which were varied in these simulations against known values. (B) Estimates
    of \gls{m} and \gls{N} which were held fixed in these simulations at the
    values \gls{m} = 3 and \gls{N} = 5000.
  }        
  \label{fig:abcptm3}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics{abc-point-estimate-m4.pdf}
  \caption[
    \Acrlong{MAP} point estimates for \gls{BA} model parameters obtained by
    running \software{netabc} on simulated data, for simulations with \gls{m} = 3.
  ]{
    \Acrlong{MAP} point estimates for \gls{BA} model parameters obtained by
    running \software{netabc} on simulated data, for simulations with \gls{m} = 4.
    Dashed lines indicate true values. (A) Estimates of \gls{alpha} and \gls{I}
    which were varied in these simulations against known values. (B) Estimates
    of \gls{m} and \gls{N} which were held fixed in these simulations at the
    values \gls{m} = 4 and \gls{N} = 5000.
  }        
  \label{fig:abcptm4}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics{sir-trajectories.pdf}
  \caption[Average trajectories of epidemics simulated according to the
  \gls{SIR} model over full and \gls{BA} networks.]
  {
      Average trajectories of epidemics simulated according to the \gls{SIR}
      model over full and \gls{BA} networks. 100 epidemics each were simulated
      over completely connected networks and networks generated from the
      \gls{BA} model. The network parameters were $\alpha = 1$ and $m = 2$.
      The transmission rate along each edge of a network $G$ was taken as
      $2/|E(G)|$, and the removal rate of each vertex was taken as $1/|V(G)|$.
      These choices ensured that both networks had the same waiting time until
      the next transmission at the beginning of the epidemic.
  }
  \label{fig:sir}
\end{figure}

@@

\begin{figure}[ht]
  \includegraphics{realdata-hpd-bc-m2}
  \vspace{8pt}
  \caption[
      Maximum \textit{a posteriori} point estimates and 95\% HPD intervals for
      parameters of the BA network model, fitted to five published HIV datasets
      with \software{netabc} using the prior $m \sim DiscreteUniform(2, 5)$.
  ]{
      Maximum \textit{a posteriori} point estimates and 95\% HPD intervals for
      parameters of the BA network model, fitted to five published HIV datasets
      with \software{netabc} using the prior $m \sim$ DiscreteUniform(2, 5).
      $x$-axes indicate regions of nonzero prior density. In particular, the
      prior on $m$ was DiscreteUniform(2, 5).
  }
  \label{fig:abchpdm2}
\end{figure}

\begin{figure}[H]
  \includegraphics{bctree-posterior}
  \caption[
      Approximate marginal posterior distributions of BA model parameters for
      BC data.
  ]
  {
      Approximate marginal posterior distributions of BA model parameters for
      BC data. Vertical lines indicate maximum \textit{a posteriori} estimates,
      and shaded areas are 95\% highest posterior density intervals. $x$-axis
      indicates regions of nonzero prior density.
  }
  \label{fig:bctree}
\end{figure}

\begin{figure}[H]
  \includegraphics{cuevas2009-posterior}
  \caption[
      Approximate marginal poosterior distributions of BA model parameters for
      \textcite{cuevas2009hiv} data. 
  ]{
      Approximate marginal poosterior distributions of BA model parameters for
      \textcite{cuevas2009hiv} data. Vertical lines indicate maximum \textit{a
      posteriori} estimates, and shaded areas are 95\% highest posterior
      density intervals. $x$-axis indicates regions of nonzero prior density.
  }
  \label{fig:cuevas}
\end{figure}

\begin{figure}[H]
  \includegraphics{li2015-posterior}
  \caption[
      Approximate marginal posterior distributions of BA model parameters for
      \textcite{li2015hiv} data. 
  ]{
      Approximate marginal posterior distributions of BA model parameters for
      \textcite{li2015hiv} data. Vertical lines indicate maximum \textit{a
      posteriori} estimates, and shaded areas are 95\% highest posterior
      density intervals. $x$-axis indicates regions of nonzero prior density.
  }
  \label{fig:li}
\end{figure}

\begin{figure}[H]
  \includegraphics{niculescu2015-posterior}
  \caption[
      Approximate marginal posterior distributions of BA model parameters for
      \textcite{niculescu2015recent} data.
  ]{
      Approximate marginal posterior distributions of BA model parameters for
      \textcite{niculescu2015recent} data. Vertical lines indicate maximum
      \textit{a posteriori} estimates, and shaded areas are 95\% highest
      posterior density intervals. $x$-axis indicates regions of nonzero prior
      density.
  }
  \label{fig:niculescu}
\end{figure}

\begin{figure}[H]
  \includegraphics{novitsky2014-posterior}
  \caption[
      Approximate marginal posterior distributions of BA model parameters for
      \textcite{novitsky2013phylogenetic, novitsky2014impact} data.
  ]{
      Approximate marginal posterior distributions of BA model parameters for
      \textcite{novitsky2013phylogenetic, novitsky2014impact} data. Vertical
      lines indicate maximum \textit{a posteriori} estimates, and shaded areas
      are 95\% highest posterior density intervals. $x$-axis indicates regions
      of nonzero prior density.
  }
  \label{fig:novitsky}
\end{figure}

\begin{figure}[H]
  \includegraphics{wang2015-posterior}
  \caption[
      Approximate marginal posterior distributions of BA model parameters for
      \textcite{wang2015targeting} data.
  ]{
      Approximate marginal posterior distributions of BA model parameters for
      \textcite{wang2015targeting} data. Vertical lines indicate maximum
      \textit{a posteriori} estimates, and shaded areas are 95\% highest
      posterior density intervals. $x$-axis indicates regions of nonzero prior
      density.
  }
  \label{fig:wang}
\end{figure}

<<abc_posterior, echo=FALSE, results="asis">>=
    N <- 5000
    replicate <- 0
    for (m in c(2, 3, 4)) {
    for (I in c(1000, 2000)) {
    for (alpha in c(0, 0.5, 1, 1.5)) {
        fn <- sprintf("{abc-posterior/%.1f_%d_%d_%d_%d}.pdf", alpha, I, m, N, replicate)
        lab <- sprintf("fig:%.1f-%d-%d-%d-%d", alpha, I, m, N, replicate)
        cat("\\begin{figure}[H]\n")
        cat("\\centering\n")
        cat(paste0("\\includegraphics{", fn, "}\n"))
        cat(sprintf("\\caption[Approximate marginal posterior distributions of BA model parameters for a simulated transmission tree with $\\alpha$ = %.1f, $I$ = %d, $m$ = %d, and $N$ = %d.]{\n", alpha, I, m, N))
        cat(sprintf("Approximate marginal posterior distributions of BA model parameters obtained by applying \textit{netabc} to a simulated transmission tree with BA parameter values $alpha$ = %.1f, $I$ = %d, $m$ = %d, and $N$ = %d. Vertical dashed lines indicate true values. Shaded areas are 95\\%% highest posterior density intervals. $x$-axes indicate regions of nonzero prior density.\n", alpha, I, m, N))
        cat("}\n")
        cat(paste0("\\label{", lab, "}\n"))
        cat("\\end{figure}\n")
        cat("\\clearpage\n\n")
    }
    }
    }
@
